Analysis of competitive surfing tournaments with generalized Bradley-Terry likelihoods

### 2025-12-12 inst/surfing_jsa.tex
various changes to maintain the surfing work

@@

Paired comparisons are particularly favourable to Bradley-Terry
because the likelihood function is exponential family and as such is
amenable to analysis via general linear models~\citep{turner2012}.
However, this is not applicable when more than two entities are
compared; and indeed here we see comparisons between three surfers
and, in the case of Jeep Surf Freshwater Pro WCT08, many more.  It
is natural to ask how much information is contained in the
observations where more than two surfers are in the water.

@@

\bibliographystyle{agsm}
\bibliography{chess}

>>>>

(this document is based on \citep{driver2023}).

@@

Paired comparisons are particularly favourable to Bradley-Terry
because the likelihood function is exponential family and as such is
amenable to analysis via general linear models~\citep{turner2012_nomarkup}.
However, this is not applicable when more than two entities are
compared; and indeed here we see comparisons between three surfers
and, in the case of Jeep Surf Freshwater Pro WCT08, many more.  It
is natural to ask how much information is contained in the
observations where more than two surfers are in the water.

@@

\bibliographystyle{agsm}
\bibliography{hyper2}
